Supplement to Automatic Matching of Bullet Lands

### 2016-11-30 imaging-paper.Rnw
Rebuild both papers with no cache

\subsection{Algorithm}\label{sec:algorithm}
<<twolands100, cache=TRUE,  echo=FALSE>>=
images <- file.path(datadir, dir(datadir))
images <- images[grep(" ", images)]

@@

<<twolands100match, cache=TRUE, echo=FALSE, dependson='twolands100'>>=
matches <- lofX %>% group_by(y) %>% summarise(
  potential = (length(unique(type)) == 1),
  allnas = sum(is.na(type))/n(),
  type1 = na.omit(type)[1],
  type = paste(type, sep="|", collapse="|"),
  n = n()
)

@@

\begin{figure}[hbtp]
  \centering
<<crosscuts-vary-b31, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', cache=TRUE, warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
paths <- paths[grep("Br[0-9]", paths)]

>>>>

\subsection{Algorithm}\label{sec:algorithm}
<<twolands100,  echo=FALSE>>=
images <- file.path(datadir, dir(datadir))
images <- images[grep(" ", images)]

@@

<<twolands100match, echo=FALSE, dependson='twolands100'>>=
matches <- lofX %>% group_by(y) %>% summarise(
  potential = (length(unique(type)) == 1),
  allnas = sum(is.na(type))/n(),
  type1 = na.omit(type)[1],
  type = paste(type, sep="|", collapse="|"),
  n = n()
)

@@

\begin{figure}[hbtp]
  \centering
<<crosscuts-vary-b31, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', warning = FALSE>>=
paths <- file.path(datadir, dir(datadir))
paths <- paths[grep("Br[0-9]", paths)]

### 2016-11-30 imaging-supplement.Rnw
Rebuild both papers with no cache

<<bullet1, echo=FALSE, cache=TRUE>>=
db1 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 1-%d.x3p"), i)
  dbi <- fortify_x3p(read_x3p(bname))
  dbi$part <- i
  db1 <- rbind(db1, dbi)
}

@@

<<bullet2, echo=FALSE, cache=TRUE>>=
db2 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 2-%d.x3p"), i)
  dbi <- fortify_x3p(read_x3p(bname))
  dbi$part <- i
  db2 <- rbind(db2, dbi)
}

@@

Figure~\ref{fig:crosscuts} shows a sequence of signatures for bullet 1-5 (barrel 1) that are taken at heights 50$\mu m$ apart, between 150$\mu m$  and 400$\mu m$. These are compared to the signature at a height of 100$\mu m$. Initially, this comparison constitutes an almost perfect match between the two signatures. However, the match quickly deteriorates with increasing distance between the heights at which signatures are extracted.  Only if signatures are from heights  within 150$\mu m$ do we get a good visual match even when we know that the same bullet surface is being used. 
Given that we have to expect some variation in nominally the same height values due to (manual) alignments in microscopes, we should take height values into account in the automatic matching routine by evaluating matches at several heights. 
\begin{figure}[hbtp]
  \centering
<<crosscuts-vary, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', cache=TRUE, warning = FALSE>>=

@@

<<aligned, echo=FALSE, warning=FALSE,  cache=TRUE>>=
matches <- read.csv("csvs/matches-old.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br.* Bullet ", "", mm$value)
mm$prefix <- sprintf("Br%d Bullet ", mm$barrel)
unkns <- grep("[A-Z]",mm$value)
mm$prefix[unkns] <- "Ukn Bullet "
mm$path <- "images/Hamby (2009) Barrel/bullets/"
mm$path <-   with(mm, paste0(path, prefix, value, ".x3p"))

>>>>

<<bullet1, echo=FALSE>>=
db1 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 1-%d.x3p"), i)
  dbi <- fortify_x3p(read_x3p(bname))
  dbi$part <- i
  db1 <- rbind(db1, dbi)
}

@@

<<bullet2, echo=FALSE>>=
db2 <- NULL
for (i in 1:6) {
  bname <- sprintf(file.path(datadir, "Br1 Bullet 2-%d.x3p"), i)
  dbi <- fortify_x3p(read_x3p(bname))
  dbi$part <- i
  db2 <- rbind(db2, dbi)
}

@@

Figure~\ref{fig:crosscuts} shows a sequence of signatures for bullet 1-5 (barrel 1) that are taken at heights 50$\mu m$ apart, between 150$\mu m$  and 400$\mu m$. These are compared to the signature at a height of 100$\mu m$. Initially, this comparison constitutes an almost perfect match between the two signatures. However, the match quickly deteriorates with increasing distance between the heights at which signatures are extracted.  Only if signatures are from heights  within 150$\mu m$ do we get a good visual match even when we know that the same bullet surface is being used. 
Given that we have to expect some variation in nominally the same height values due to (manual) alignments in microscopes, we should take height values into account in the automatic matching routine by evaluating matches at several heights. 
\begin{figure}[hbtp]
  \centering
<<crosscuts-vary, echo=FALSE, fig.width = 12, fig.height = 7, out.width = '\\textwidth', warning = FALSE>>=

@@

<<aligned, echo=FALSE, warning=FALSE>>=
matches <- read.csv("csvs/matches-old.csv", header = FALSE)
matches$barrel <- rep(1:10, each=6)
matches$id <- 1:nrow(matches)
mm <- melt(matches, id.var=c("barrel", "id"), na.rm=TRUE)
mm <- subset(mm, value != "")
mm$value <- gsub("Br.* Bullet ", "", mm$value)
mm$prefix <- sprintf("Br%d Bullet ", mm$barrel)
unkns <- grep("[A-Z]",mm$value)
mm$prefix[unkns] <- "Ukn Bullet "
mm$path <- "images/Hamby (2009) Barrel/bullets/"
mm$path <-   with(mm, paste0(path, prefix, value, ".x3p"))
